---
title: "Set GeoJSON properties from CSV attributes"
author: "Florian Mayer"
date: "12/01/2015"
output: html_document
---
```{r, echo=FALSE}
# devtools::install_github("rstudio/leaflet")
library(leaflet)
library(rjson)
```

## Data
Consider a GeoJSON file of sites with a site name, and a CSV file of site 
attributes.

The GeoJSON corresponds to an ESRI Shapefile with only names, 
but no other attributes set.
The CSV file corresponds to the attribute table of the Shapefile.

```{r}
dataset_url <- paste0("http://internal-data.dpaw.wa.gov.au/dataset/",
                      "0ca68dd5-57b1-4332-beae-ae0a5b9ed762/")

csv_url <- paste0(dataset_url,
                  "resource/46b6b5d6-e476-4876-93e4-3c5215ed5a6e/",
                  "download/Jurieninvertebratesurveysitelist.csv")
csv <- read.csv(csv_url, header=T, stringsAsFactor=F, 
                col.names=c("name", "description", "wetland_style", 
                            "sampled_on", "Latitude", "Longitude"))

gj_url <- paste0(dataset_url,
                 "resource/6d13c10b-fb88-433a-9133-84061351079c/",
                 "download/Jurienaquaticinvertebratesurveysites.json")
gj <- fromJSON(file=gj_url)
```
The csv is now loaded as `data.frame`, while the GeoJSON is a nested `list`.

## Process
In a loop over `gj$features$properties`, new and existing properties can be set 
from the csv file where names match.
```{r}
for (i in 1:length(gj$features)){
  n <- gj$features[[i]]$properties$Name
  textdata <- csv[which(csv$name==n),]
  gj$features[[i]]$properties$description <- textdata$description
  gj$features[[i]]$properties$wetland_style <- textdata$wetland_style
  gj$features[[i]]$properties$sampled_on <- textdata$sampled_on
  gj$features[[i]]$properties$popup <-  paste0(
      "<h3>", textdata$name, "</h3>",
      "<p>", textdata$description, "</p>",
      "<p><strong>Wetland  style</strong> ", textdata$wetland_style, "</p>",
      "<p><strong>Sampled on</strong> ", textdata$sampled_on, "</p>")
}
```

## Result
The resulting, modified GeoJSON object now contains attributes from the csv file,
as shown in this map. The property `popup` contains the HTML of the popups.
```{r}
m = leaflet() %>% 
  addTiles(
    paste0('http://server.arcgisonline.com/ArcGIS/rest/services/',
            'World_Topo_Map/MapServer/tile/{z}/{y}/{x}'),
    attribution = paste('Tiles &copy; Esri &mdash; Esri, DeLorme, NAVTEQ,',
                        'TomTom, Intermap, iPC, USGS, FAO, NPS, NRCAN, GeoBase,',
                        ' Kadaster NL, Ordnance Survey, Esri Japan, METI,',
                        'Esri China (Hong Kong), and the GIS User Community')) %>%
  setView(120, -25, zoom = 5) %>%
  addGeoJSON(gj, layerId="gj")
m
```

## Output
The CSV and the GeoJSON can now be saved and re-uploaded. If the original names 
are retained, the URLs used in this example will remain unchanged.
```{r}
write.csv(csv, file='tmp/Jurieninvertebratesurveysitelist.csv', row.names=F)
write(toJSON(gj), file='tmp/Jurienaquaticinvertebratesurveysites.json')
```

## Version control
This RMarkdown workbook is maintained at [github](https://github.com/florianm/cleanR).
